Presentation Title

### 2017-07-17 thesis/chapters/ch3-model.tex
Write more design variations

\chapter{System Architecture}
\label{ch:model}

@@

\section{System Overview}
\label{sec:system-overview}
The system consist of one data structure---Extended TrustChain,
and three protocols---consensus protocol, transaction protocol and validation protocol.
We first describe each component individually and then explain how they fit together in \Cref{sec:combined-protocol}.

@@

\subsection{Consensus Protocol}\label{sec:overview-cons}

@@

\subsection{Transaction and Validation}
The TX protocol is a simple request and response protocol.
The nodes exchange one round of messages and create new TX blocks on their respective chains.
Thus, as we mentioned before, one transaction should result in two TX blocks.

@@

\subsection{Combined Protocol}
\label{sec:combined-protocol}
The final protocol is essentially the concurrent composition of the three aforementioned protocols,
all making use the Extended TrustChain data structure.

@@

\section{Model and Assumptions}
\label{sec:model-assumptions}

@@

\subsection{Transaction Block}
The TX block is a six-tuple, i.e $t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), seq_u, txid, pk_v, m, sig_u \rangle$.
We describe each item in turn.
\begin{enumerate}
\item $\textsf{H}(b_{u, i - 1})$ is the hash pointer to the previous block.
\item $seq_u$ is the sequence number which should equal $i$.
\item $txid$ is the transaction identifier, it should be generated using a cryptographically secure pseudo-random number generator by the initiator of the transaction.
\item $pk_v$ is the public key of the counterparty $v$.
\item $m$ is the transaction message.
\item $sig_u$ is the signature created using $sk_u$ on the concatination of the binary representation of the five items above.
\end{enumerate}
The fact that we have no constraint on the content of $m$ is in alignment with our design goal---application neutrality.

@@

\subsection{Checkpoint Block}

@@

\subsection{Consensus Result}
\label{sec:consensus-result}
Our consensus protocol runs in rounds as discussed in \Cref{sec:system-overview}.
Every round is identified by a round number $r$, which is incremented on every new round.
The consensus result is a tuple, i.e. $\C_r = \langle r, C \rangle$,
where $C$ is a set of CP blocks agreed by the facilitators of round $r$.

\subsection{Chain Properties}
Here we define a few important properties which results from the interleaving nature of CP and TX blocks.

@@

\section{Consensus Protocol}
\label{sec:cons-protocol}

@@

\subsection{Background on Asynchronous Subset Consensus}
\label{sec:acs-background}

@@

\subsection{Bootstrap Phase}
\label{sec:bootstrap}
Now we have all the necessary information to describe our consensus protocol.
We begin with the bootstrap phase and then move onto the actual consensus phase.

@@

\subsection{Consensus Phase}
\label{sec:consensus-phase}
The consensus phase begins when $\F_r$ is available to all the nodes.
Note that $\F_r$ indicates the facilitators that were elected using result of round $r$ and are responsible for driving the ACS protocol in round $r + 1$.
The goal is to reach agreement on a set of new facilitators $\F_{r + 1}$ that satisfies the four properties in \Cref{def:consensus}.

@@

\subsection{Relationship with $\alpha$-Synchroniser}
TODO

\section{Transaction Protocol}
\label{sec:tx-protocol}

@@

\section{Validation Protocol}
\label{sec:vd-protocol}

@@

\subsection{Validity Definition}
A transaction can be in one of three states in terms of validity---\emph{valid}, \emph{invalid} and \emph{unknown}.
Given a fragment $F_{v, j}$, the validity of the transaction $t_{u, i}$ is captured by the function $\textsf{get\_validity}(t, F)$ (\Cref{alg:get-validity}).
The first four conditions (up to \Cref{line:valid-fragment}) essentially check whether the fragment is the one that the verifier needs.
If it is not, then the verifier cannot make any decision and return \emph{unknown}.
This is likely to be the case for new transactions because $\textsf{agreed\_fragment}(\cdot)$ would be $\bot$.
The next two conditions checks for tampering or missing blocks, if any of these misconducts are detected, then the TX is invalid.

@@

    \If{$|F_{v, j}| > L$}
        \State \Return \emph{unknown}
    \EndIf \Comment fragment not too long
    \State

@@

\subsection{Validation Protocol}
With the validity definition, we are ready to construct a protocol for determining the validity of transactions.
The protocol is a simple response and request protocol (\Cref{alg:vd-proto}).
If $u$ wishes to validate some TX with ID $txid$ and counterparty $v$, it sends $\langle \texttt{vd\_req}, txid \rangle$ to $v$.
The desired properties of the validation protocol are as follows.
\begin{definition}
\label{def:validation}
\textbf{\emph{Properties of the validation protocol}}

@@

Up to this point,
we have discussed our protocol in the context of the model and assumptions defined in \Cref{sec:model-assumptions}.
In this section, 
we explore a few design variations which we can make if we relax our model.
These variations do not have the same theoretical elegance as our original model.
But they enable better performance, allow us to apply our design in the fully permissionless setting and improves privacy.

@@

\subsection{Privacy preserving validation protocol}
TODO

\subsection{Caching agreed fragments}

\subsection{Global probabilistic fork detection}
TODO

>>>>

\chapter{System architecture}
\label{ch:model}

@@

\section{System overview}
\label{sec:system-overview}
The system consist of one data structure---Extended TrustChain,
and three protocols---consensus protocol, transaction protocol and validation protocol.
We first describe each component individually and then explain how they fit together in \Cref{sec:combined-protocol}.

@@

\subsection{Consensus protocol}\label{sec:overview-cons}

@@

\subsection{Transaction and validation}
The TX protocol is a simple request and response protocol.
The nodes exchange one round of messages and create new TX blocks on their respective chains.
Thus, as we mentioned before, one transaction should result in two TX blocks.

@@

\subsection{Combined protocol}
\label{sec:combined-protocol}
The final protocol is essentially the concurrent composition of the three aforementioned protocols,
all making use the Extended TrustChain data structure.

@@

\section{Model and assumptions}
\label{sec:model-assumptions}

@@

\subsection{Transaction block}
The TX block is a six-tuple, i.e $t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), seq_u, txid, pk_v, m, sig_u \rangle$.
We describe each item in turn.
\begin{enumerate}
\item $\textsf{H}(b_{u, i - 1})$ is the hash pointer to the previous block.
\item $seq_u$ is the sequence number which should equal $i$.
\item $txid$ is the transaction identifier, it should be generated using a cryptographically secure pseudo-random number generator by the initiator of the transaction.
\item $pk_v$ is the public key of the counterparty $v$.
\item $m$ is the transaction message.
\item $sig_u$ is the signature created using $sk_u$ on the concatination of the binary representation of the five items above.
\end{enumerate}
The fact that we have no constraint on the content of $m$ is in alignment with our design goal---application neutrality.

@@

\subsection{Checkpoint block}

@@

\subsection{Consensus result}
\label{sec:consensus-result}
Our consensus protocol runs in rounds as discussed in \Cref{sec:system-overview}.
Every round is identified by a round number $r$, which is incremented on every new round.
The consensus result is a tuple, i.e. $\C_r = \langle r, C \rangle$,
where $C$ is a set of CP blocks agreed by the facilitators of round $r$.

\subsection{Chain properties}
Here we define a few important properties which results from the interleaving nature of CP and TX blocks.

@@

\section{Consensus protocol}
\label{sec:cons-protocol}

@@

\subsection{Background on asynchronous subset consensus}
\label{sec:acs-background}

@@

\subsection{Bootstrap phase}
\label{sec:bootstrap}
Now we have all the necessary information to describe our consensus protocol.
We begin with the bootstrap phase and then move onto the actual consensus phase.

@@

\subsection{Consensus phase}
\label{sec:consensus-phase}
The consensus phase begins when $\F_r$ is available to all the nodes.
Note that $\F_r$ indicates the facilitators that were elected using result of round $r$ and are responsible for driving the ACS protocol in round $r + 1$.
The goal is to reach agreement on a set of new facilitators $\F_{r + 1}$ that satisfies the four properties in \Cref{def:consensus}.

@@

\subsection{Relationship with $\alpha$-synchroniser}
TODO

\section{Transaction protocol}
\label{sec:tx-protocol}

@@

\section{Validation protocol}
\label{sec:vd-protocol}

@@

\subsection{Validity definition}
A transaction can be in one of three states in terms of validity---\emph{valid}, \emph{invalid} and \emph{unknown}.
Given a fragment $F_{v, j}$, the validity of the transaction $t_{u, i}$ is captured by the function $\textsf{get\_validity}(t, F)$ (\Cref{alg:get-validity}).
The first four conditions (up to \Cref{line:valid-fragment}) essentially check whether the fragment is the one that the verifier needs.
If it is not, then the verifier cannot make any decision and return \emph{unknown}.
This is likely to be the case for new transactions because $\textsf{agreed\_fragment}(\cdot)$ would be $\bot$.
The next two conditions checks for tampering or missing blocks, if any of these misconducts are detected, then the TX is invalid.

@@

    % \If{$|F_{v, j}| > L$}
    %     \State \Return \emph{unknown}
    % \EndIf \Comment fragment not too long
    % \State

@@

\subsection{Validation protocol}
With the validity definition, we are ready to construct a protocol for determining the validity of transactions.
The protocol is a simple response and request protocol (\Cref{alg:vd-proto}).
If $u$ wishes to validate some TX with ID $txid$ and counterparty $v$, it sends $\langle \texttt{vd\_req}, txid \rangle$ to $v$.
The desired properties of the validation protocol are as follows.
\begin{definition}
\label{def:validation}
\textbf{\emph{Properties of the validation protocol}}

@@

Up to this point,
we have discussed our protocol in the context of the model and assumptions defined in \Cref{sec:model-assumptions}.
In this section, 
we explore a few design variations which we can make, some of them require a relaxed version of our original model.
They enable better performance, allow us to apply our design in the fully permissionless setting and improves privacy.

@@

\subsection{Privacy preserving validation protocol using compact blocks}
\label{sec:compact}
Our approach already has privacy preserving features in comparison to early blockchain systems.
That is, the transactions for each node are only revealed during the validation protocol.
Hence if two nodes never directly or indirectly interact with each other,
their transactions are never revealed.

We can take our privacy-preserving property one step further by introducing another level of hash pointer indirection.
The result is shown in~\Cref{fig:compact}.
\begin{figure}
    \includegraphics[width=0.7\textwidth]{compact}
    \centering
    \caption{The chain on the left represent direct chaining, where the digest in ``Prev'' is simply the digest of the previous block.
    The chain on the right uses compact blocks, represented by the smaller squares.
    Compact blocks also form a chain as before, but they each have a hash pointer to the full block, identified by ``Seq'' or ``Digest''.}
    \label{fig:compact}
\end{figure}

Concretely, we introduce an additional block type,
namely compact block.
Such blocks only have three attributes,
\begin{enumerate}
\item Seq---the sequence number its corresponding block,
\item Digest---the digest of its corresponding block, and
\item Prev---the digest of the previous compact block.
\end{enumerate}
Each compact block has a corresponding full block (either a CP block or a TX block).
The relationship is uniquely identified with Seq or Digest.
Recall that our original validation protocol requires the nodes to send the full agreed fragment.
With compact blocks, it is only necessary to send the compact version of the agreed fragment.
The validation then proceeds in a similar fashion,
provided that the pair of the to-be-validated TX block is known.

The space saving of this approach of course depends on the size of the full blocks.
If the full blocks are on average 500 bytes
(which is the typical size of Bitcoin transactions ~\cite{txsize}),
and the compact blocks are $32 + 32 + 8 = 72$ bytes
(SHA256 digests are 32 bytes each and we use a 64 bit integer to represent the sequence number),
then we have a 86\% saving in communication cost.

%Using compact blocks, it is possible to reduce network communication costs in the validation protocol but also protect transaction privacy.

\subsection{Optimising validation protocol using cached agreed fragments}
\label{sec:caching}
One more way to improve the efficiency of the validation protocol is to use a single agreed fragment to validate multiple transaction.
Concretely, upon receiving an agreed fragment from node $A$,
rather than validating a single transaction,
we attempt to validate all transactions in the unknown state performed with $A$ in that fragment.

For a node, the benefit of this technique is maximised when it only transacts with one other node.
In this case, the communication of one fragment is sufficient to validate all transactions in that fragment.
In the opposite extreme, if every transaction that the node makes is with another unique node,
then the caching mechanism would have no effect.

\subsection{Global fork detection}
The validation algorithm guarantees that there are no forks within a single agreed fragment.
This is sufficient for some applications such as proving the existance of some information.
However, applications such as digital cash where every block depends on some previous block,
then our scheme is not suitable.

There are a variety of approaches to do global fork detection.
First and the easiest solution is to simply ask for every agreed fragment from the one containing the genesis block up to the one that the to-be-proven TX block is in.
If the hash pointers are correct and all the CP blocks are in consensus, then the verifier can be sure that there are no forks.
We use this approach in our prior work on Implicit Consensus~\cite{implicitconsensus}.
It may sound inefficient at first, but nodes can employ caching to minimise communication costs.
In our work we call this ``spontaneous sharding''.

The second approach is probabilistic but with only a constant communication overhead.
For a node, observe that if every of its agreed fragment has a transaction with a honest node,
then the complete chain is effectively validated in a distributed maner.
The only way for an attacker to make a fork is to make sure that the agreed fragment containing the fork has no transactions with honest nodes.
We claim such malicious behaviour is prevented probabilisticaly using a challenge-response protocol as follows.
Suppose node $A$ wish to make a transaction with node $B$.
$A$ first sends a challenge to $B$ asking it to proof that it holds a valid agreed fragment between some consensus round specified by $A$.
If $B$ provides a correct proof, then they run the transaction protocol as usual.
If $B$ provides an invalid proof or refuses to respond,
then $A$ would refuse to make the transaction.
The probability that an honest node catches out a malicious node is 
$$p = \frac{f}{r},$$
where $f$ is the number of bad agreed fragments and $r$ is the latest round number.
If there are more nodes (say $n$) trying to make transactions with the malicious node,
then the probability that the malicious node does gets caught at least once follows a binomial distribution
$$\Pr[X > 0] = \sum_{k = 1}^{n}\binom{n}{k}p^k (1 - p)^{n - k}.$$

% subtlety when fork happens on CP block

### 2017-07-17 thesis/chapters/ch4-analysis.tex
Fix up implementation section
Write more design variations

\chapter{Analysis of Correctness and Performance}
\label{ch:analysis}

@@

\section{Correctness in the Presense of Faults}
Our first objective is to show that \Cref{def:consensus} holds for our consensus protocol.
Then, building on top of it, we show \Cref{def:validation} holds for the validation protocol.
The resulting theorem shows that only using CP blocks in the consensus algorithm implies consensus on TX blocks,
in other words, implicit consensus.

@@

\subsection{Analysis of the Consensus Protocol}

@@

\subsection{Correctness of Validation}
The consensus protocol (on CP blocks and facilitators) is the backbone for consensus on transactions.
In this section we build on top of \Cref{theorem:consensus} to show that most (except liveness) properties in \Cref{def:validation} can be satisfied.

@@

\subsection{Impossibility of Liveness}
While \Cref{theorem:validation-agreement} is a major result that allows significantly improved performance over traditional blockchain systems,
it is not perfect.
Now we show a negative result, where the liveness property of \Cref{def:validation} cannot be attained.
Meaning that trasanctions with adversaries cannot always be validated.

@@

\section{Performance}
\label{sec:performance-analysis}
This section aims to analytically answer our research question.
That is, does the global throughput increase linearly with respect to the population size?
We begin by looking at the communication and time complexity of the consensus protocol,
and then the bandwidth requirement for a single transaction.
We build on top of those results to analyse do the global throughput analysis.

@@

\subsection{Communication Cost for Transactions}
\label{sec:communication-cost-for-tx}
With the analysis on the duration of the consensus protocol,
we are ready to analyse the amount of data required to be transmitted over a link per transaction,
which we call the communication cost per transaction.
% First, we define bandwidth as the ``amount of data a link or network path can deliver per unit of
% time''~\cite{prasad2003bandwidth}.
We know that to create and then validate a transaction,
the communication cost per transaction is of $O(l)$,
where $l$ is the length of the agreed fragment.
This can be seen from the fact that the largest message by far is the \texttt{vd\_resp} message,
which contains the agreed fragment.
The other messages (\texttt{tx\_req}, \texttt{tx\_resp} and \texttt{vd\_req}) are constant factors.
If we assume that every node performs transactions at a constant rate of $r_{\text{tx}}$ per second.
Then
$$l = r_{\text{tx}} D_{\text{c}},$$
where $D_{\text{c}}$ is the duration a round of the consensus protocol.
But from \Cref{sec:cons-duration},
we know that $D_{\text{c}}$ is of $O(N)$, thus the communication cost per transaction is $O(N)$.
This is intuitive because round duration would be longer if there are more CP blocks (more $N$), which means that the agreed fragments are longer (assuming nodes transact at a constant rate).
The behaviour is also verified experimentally in \Cref{ch:implementation}.

\subsection{Global Throughput}
\label{sec:global-throughput}
Using our results so far, we are able to analyse the global throughput.
First we clarify the bandwidth definition, which is ``the data rate at which a network link or a network path can transfer''~\cite{prasad2003bandwidth}.
Now, suppose every node has some fixed bandwidth per link $C$ and $N$ links.
They also make transactions at $r_{\text{tx}}$ per second.
Then we have the inequality
$$NC \ge r_{\text{tx}} l,$$
where $l$ is the length of the the agree fragment as before.
The inequality suggests that the rate for which transactions and validations are made cannot exceed the total bandwidth of all the links.

@@

\section{Effect of A Highly Adverserial Environment}

>>>>

\chapter{Analysis of correctness and performance}
\label{ch:analysis}

@@

\section{Correctness in the presense of faults}
Our first objective is to show that \Cref{def:consensus} holds for our consensus protocol.
Then, building on top of it, we show \Cref{def:validation} holds for the validation protocol.
The resulting theorem shows that only using CP blocks in the consensus algorithm implies consensus on TX blocks,
in other words, implicit consensus.

@@

\subsection{Analysis of the consensus protocol}

@@

\subsection{Correctness of validation}
The consensus protocol (on CP blocks and facilitators) is the backbone for consensus on transactions.
In this section we build on top of \Cref{theorem:consensus} to show that most (except liveness) properties in \Cref{def:validation} can be satisfied.

@@

\subsection{Impossibility of liveness}
While \Cref{theorem:validation-agreement} is a major result that allows significantly improved performance over traditional blockchain systems,
it is not perfect.
Now we show a negative result, where the liveness property of \Cref{def:validation} cannot be attained.
Meaning that trasanctions with adversaries cannot always be validated.

@@

\section{Performance analysis}
\label{sec:performance-analysis}
This section aims to analytically answer our research question.
That is, does the global throughput increase linearly with respect to the population size?
We begin by looking at the communication and time complexity of the consensus protocol,
and then the bandwidth requirement for a single transaction.
We build on top of those results to analyse do the global throughput analysis.

@@

\subsection{Communication cost for transactions}
\label{sec:communication-cost-for-tx}
With the analysis on the duration of the consensus protocol,
we are ready to analyse the amount of data required to be transmitted over a link per transaction,
which we call the communication cost per transaction.
% First, we define bandwidth as the ``amount of data a link or network path can deliver per unit of
% time''~\cite{prasad2003bandwidth}.
We know that to create and then validate a transaction,
the communication cost per transaction is of $O(l)$,
where $l$ is the length of the agreed fragment.
This can be seen from the fact that the largest message by far is the \texttt{vd\_resp} message,
which contains the agreed fragment.
The other messages (\texttt{tx\_req}, \texttt{tx\_resp} and \texttt{vd\_req}) are constant factors.
If we assume that every node performs transactions at a constant rate of $r_{\text{tx}}$ per second.
Then
$$l = r_{\text{tx}} D_{\text{c}},$$
where $D_{\text{c}}$ is the duration a round of the consensus protocol.
But from \Cref{sec:cons-duration},
we know that $D_{\text{c}}$ is of $O(N)$, thus the communication cost per transaction is $O(N)$.
This is intuitive because round duration would be longer if there are more CP blocks (more $N$), which means that the agreed fragments are longer (assuming nodes transact at a constant rate).
The behaviour is also verified experimentally in \Cref{ch:implementation}.

\subsection{Global throughput}
\label{sec:global-throughput}
Using our results so far, we are able to analyse the global throughput.
First we clarify the bandwidth definition, which is ``the data rate at which a network link or a network path can transfer''~\cite{prasad2003bandwidth}.
Now, suppose every node has some fixed bandwidth per link $C$ and $N$ links.
They also make transactions at $r_{\text{tx}}$ per second.
Then we have the inequality
$$NC \ge r_{\text{tx}} l,$$
where $l$ is the length of the the agree fragment as before.
The inequality suggests that the rate for which transactions and validations are made cannot exceed the total bandwidth of all the links.

@@

\section{Effect of a highly adverserial environment}

### 2017-07-17 thesis/chapters/ch5-implementation.tex
Write more design variations

\chapter{Implementation and Experimental Results}
\label{ch:implementation}

@@

The prototype implementation can be found on GitHub.
\begin{displayquote}
\url{https://github.com/kc1212/consensus-thesis-code}
\end{displayquote}
It is written in the event driven paradigm, using the Python programming language\footnote{\url{https://www.python.org/}}.
We use the Twisted\footnote{\url{https://twistedmatrix.com/}} library for networking.

@@

\section{Experimental Setup}
\label{sec:experimental-setup}

@@

\section{Global Throughput}
\begin{figure}[h]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/throughput-vs-population}
    \caption{Transactions are with fixed neighbours.}
    \label{fig:global-throughput-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/throughput-vs-population}
    \caption{Transactions are with random neighbours.}
    \label{fig:global-throughput-random}
  \end{subfigure}
  }
  \caption{Global throughput}
  \label{fig:global-throughput}
\end{figure}

>>>>

\chapter{Implementation and experimental results}
\label{ch:implementation}

@@

The prototype implementation can be found on GitHub.
\begin{displayquote}
\url{https://github.com/kc1212/consensus-thesis-code}
\end{displayquote}
It implements the three protocols and the Extended TrustChain discussed in~\Cref{ch:model}.
We also implement two optimisations---privacy preserving validation protocol using compact blocks (\Cref{sec:compact})
and optimised validation protocol using cached agreed fragments (\Cref{sec:caching}).
It is written in the event driven paradigm, using the Python programming language\footnote{\url{https://www.python.org/}}.
We use the Twisted\footnote{\url{https://twistedmatrix.com/}} library for networking.

@@

\section{Experimental setup}
\label{sec:experimental-setup}

@@

\section{Global throughput}
\begin{figure}[h]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/throughput-vs-population}
    \caption{Transactions are with fixed neighbours.}
    \label{fig:global-throughput-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/throughput-vs-population}
    \caption{Transactions are with random neighbours.}
    \label{fig:global-throughput-random}
  \end{subfigure}
  }
  \caption{Global throughput}
  \label{fig:global-throughput}
\end{figure}

### 2017-07-17 thesis/chapters/ch6-related-work.tex
Write more design variations

\chapter{Related Work}
\label{ch:related}

@@

\section{Classical Blockchain Systems}
This category represent systems with a probabilistic probabilistic consensus algorithm.
That is, transactions never reach consensus with a probability of 1.
The typical examples are proof-of-work based systems such as Bitcoin, Ethereum and other Altcoins.
In Bitcoin, the level of consensus of a block\footnote{Note that a block in Bitcoin contain many transactions whereas our TX block only contain a single transaction.}
is determined how deep it is in the Bitcoin blockchain, also called the number of confirmation.
The probability of a block being orphaned drops exponentially as the depth increases~\cite{bitcoin}.
Nevertheless, the probability of the highest block being orphaned is non-negligible.
The advantage of this type of consensus is that it can be used in a large network and is reasonably secure.
Attackers can not out pace honest users in finding new blocks unless they have a majority of the hash power.
The disadvantage however is that transactions are never in consensus with a probability of 1---no consensus finality.
Also, the performance is limited due to the fact that blocks are of fixed size and are generated at fixed intervals.

@@

\section{Offchain Transactions}
Offchain transactions make use of the fact that, if two or more parties frequently make transactions,
then it is not necessary to store every transaction on the blockchain, only the net settlement is necessary.
The best examples are Lightning Network~\cite{lightningnetwork} and full duplex channels~\cite{decker2015fast}.
These use the Bitcoin blockchain to store the net settlement and a payment channel to conduct offchain transactions.

@@

\section{Permissioned Systems}

@@

\section{Hybrid Systems}
Hybrid systems are very recent inventions.
Just like our work, they are attempts on solving the problems of traditional blockchains.
The main characteristic of these systems is that they use a classical blockchain technique,
i.e. proof-of-work, to elect a committee and prevent Sybils.
And then they use a Byzantine consensus algorithm to actually reach consensus on a set of transactions within the committee.
Some examples are SCP~\cite{luu2015scp}, ByzCoin~\cite{kogias2016enhancing} and Solidus~\cite{abraham2016solidus}.

@@

\section{Blockchains Without Global Consensus}

>>>>

\chapter{Related work}
\label{ch:related}

@@

\section{Early blockchain systems}
This category represent systems with a probabilistic probabilistic consensus algorithm.
That is, transactions never reach consensus with a probability of 1.
The typical examples are proof-of-work based systems such as Bitcoin, Ethereum and other Altcoins.
In Bitcoin, the level of consensus of a block\footnote{Note that a block in Bitcoin contain many transactions whereas our TX block only contain a single transaction.}
is determined how deep it is in the Bitcoin blockchain, also called the number of confirmation.
The probability of a block being orphaned drops exponentially as the depth increases~\cite{bitcoin}.
Nevertheless, the probability of the highest block being orphaned is non-negligible.
The advantage of this type of consensus is that it can be used in a large network and is reasonably secure.
Attackers can not out pace honest users in finding new blocks unless they have a majority of the hash power.
The disadvantage however is that transactions are never in consensus with a probability of 1---no consensus finality.
Also, the performance is limited due to the fact that blocks are of fixed size and are generated at fixed intervals.

@@

\section{Offchain transactions}
Offchain transactions make use of the fact that, if two or more parties frequently make transactions,
then it is not necessary to store every transaction on the blockchain, only the net settlement is necessary.
The best examples are Lightning Network~\cite{lightningnetwork} and full duplex channels~\cite{decker2015fast}.
These use the Bitcoin blockchain to store the net settlement and a payment channel to conduct offchain transactions.

@@

\section{Permissioned systems}

@@

\section{Hybrid systems}
Hybrid systems are very recent inventions.
Just like our work, they are attempts on solving the problems of traditional blockchains.
The main characteristic of these systems is that they use a classical blockchain technique,
i.e. proof-of-work, to elect a committee and prevent Sybils.
And then they use a Byzantine consensus algorithm to actually reach consensus on a set of transactions within the committee.
Some examples are SCP~\cite{luu2015scp}, ByzCoin~\cite{kogias2016enhancing} and Solidus~\cite{abraham2016solidus}.

@@

\section{Blockchains without global consensus}
